\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{CormorantGaramond}
\usepackage{charter}

\setlength{\footskip}{4.1pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \scshape\large\raggedright
}{}{0em}{}[\color{black}\titlerule]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[3]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3}
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kevin Kelly} \\ \vspace{1pt}
    San Antonio, Texas, United States $|$ \href{mailto:kevinwaynekelly@gmail.com}{kevinwaynekelly@gmail.com} $|$
    \href{https://resume.kevinwaynekelly.com}{resume.kevinwaynekelly.com}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of Texas at Austin}{Aug. 2019 to May 2023}
      {Bachelor of Science in Electrical Engineering, Emphasis in Software Engineering and Design}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Applied software engineering and design principles to embedded systems, hardware design, and computer engineering projects.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
        {Formal Circuit Verification Algorithm}{}
        {Sponsored by Cadence Design Systems Inc.}
        \resumeItemListStart
          \resumeItem{Built a C++ tool with Tarjan’s SCC to detect cycle risk in RTL and ASIC netlists, enabling formal verification.}
          \resumeItem{Benchmarked alternatives and removed runtime bottlenecks, improving scalability in timing-critical netlists.}
        \resumeItemListEnd

    \resumeProjectHeading
        {Website Data Management and Deployment}{}
        {Software Keystone}
        \resumeItemListStart
          \resumeItem{Led full-stack deployment of a project management platform with React, Node.js, MongoDB, Heroku, Python, and SQL.}
          \resumeItem{Built authenticated REST APIs for secure, efficient data flow across distributed components, reducing user friction.}
          \resumeItem{Designed database schemas and backend logic for high-volume transactions, preventing data loss and contention.}
        \resumeItemListEnd

    \resumeProjectHeading
        {ARM Based USB Game Controller}{}
        {Hardware Keystone}
        \resumeItemListStart
          \resumeItem{Designed and brought up an ARM Cortex-M USB controller with dual joysticks and 12 buttons, from schematic to PCB, demonstrating SoC integration, embedded systems design, and hardware–software debugging.}
          \resumeItem{Wrote embedded C with memory-mapped I/O for deterministic control and seamless hardware–software integration.}
          \resumeItem{Validated USB HID via iterative bring up and targeted debug, yielding stable, repeatable behavior.}
        \resumeItemListEnd

    \resumeProjectHeading
        {Real Time Facial Expression Recognition}{}
        {Digital Image Processing and Machine Learning}
        \resumeItemListStart
          \resumeItem{Built a real time Python and OpenCV pipeline with Haar cascades to classify emotions in live video.}
          \resumeItem{Linked detections to smart home triggers via IoT, demonstrating end-to-end computer vision to device control.}
        \resumeItemListEnd

    \resumeProjectHeading
        {Unraid Home Server Deployment}{}
        {Personal Project}
        \resumeItemListStart
          \resumeItem{Built and maintain an Unraid server with Dockerized microservices and CI/CD pipelines for media, automation, and monitoring.}
          \resumeItem{Configured parity-protected arrays and backups to safeguard data and speed recovery, applying system administration, virtualization, VLAN, and VPN best practices.}
          \resumeItem{Improved security and performance with DNS caching, reverse proxies (NGINX/Traefik), and VPN tunneling.}
          \resumeItem{Maintain Linux VMs and containers to practice orchestration and resource isolation.}
        \resumeItemListEnd

    \resumeProjectHeading
        {Professional Portfolio Website}{}
        {Personal Project}
        \resumeItemListStart
          \resumeItem{Built and maintain a responsive, mobile-friendly portfolio highlighting projects and experience.}
          \resumeItem{Implemented CSS grid and flex layouts, plus dark mode for usability.}
          \resumeItem{Integrated OpenGraph and Twitter meta tags with SEO keywords to improve discoverability and sharing.}
          \resumeItem{Hosted on a custom domain with HTTPS for secure, dependable access.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Audio Video Assistant, Operator, Supervisor}{Sep 2019 to Aug 2023}
      {The University of Texas at Austin}{Austin, TX}
      \resumeItemListStart
        \resumeItem{Directed a 15+ technician team and trained hires on complex AV systems, networking, and real-time event operations, reducing errors in large-scale university events.}
        \resumeItem{Served as liaison for clients, performers, and university leadership, turning requirements into clear runbooks under pressure.}
        \resumeItem{Resolved technical and logistical issues in real time to ensure continuity and client success.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \item {\small
    \textbf{Programming}{: Python, Java, C, C++, C\#, JavaScript, SQL, Lua, ARM Assembly, x86 Assembly, HTML5/CSS} \\
    \textbf{Hardware / Systems}{: Verilog, RTL (Register Transfer Level) Design, Digital Logic, Formal Verification, PCB Design, Embedded Systems, SoC (System-on-Chip) Integration, System Architecture, Linux, Operating Systems, Docker, Virtualization, VLAN, VPN} \\
    \textbf{Frameworks / Tools}{: React.js, Node.js, REST APIs, OAuth, OpenCV, IoT, AWS, Git, MongoDB, PostgreSQL, Redis, CI/CD Pipelines, Unit Testing (JUnit, PyTest), Selenium, Reverse Proxies (NGINX/Traefik), TCP/IP, DNS, DHCP, RTSP, HTTP/HTTPS, SSL/TLS Certificates, Firewalls}}
 \end{itemize}

\end{document}
